\begin{thebibliography}{1}
\bibitem{ctr} ``A diagram of the CTR mode of operation''. \textit{L.A. City College}. Spring 2007. Digital Image. April 2014. \verb#<http://homepage.smc.edu/morgan_david/linsec/images/ctr.jpg>#.
\bibitem{ibm} ``An overview of the SSL or TLS handshake''. \textit{WebSphere}. IBM. March 2014. Web. April 2014.
\bibitem{nistblockciphers} ``Block Ciphers: Approved Algorithms'' \textit{National Institute of Standards and Technology}. March 2014. Web. April 2014.
\bibitem{quarkslab} Cattiaux, Cyril. ``iMessage Privacy'' \textit{Quarkslab blog}. October 2013. Web. April 2014.
\bibitem{garfinkel} Garfinkel, Simson. ``The iPhone Has Passed a Key Security Threshold''. \textit{MIT Technology Review}. August 13, 2013. Web. April 2014.
\bibitem{goodin} Goodin, Dan. ``Stop using NSA-influenced code in our products, RSA tells customers''. \textit{Ars Technica}. September 19, 2013. Web. April 2014.
\bibitem{apple} ``iOS Security''. \textit{Apple, Inc.} February 2014. Web. April 2014.
\bibitem{kakaroto} Kakaroto. ``How the ECDSA Algorithm Works.'' \textit{KaKaRoTos Blog.} N.p., n.d. Web. 23 Apr. 2014.
\bibitem{meyer} Meyer, Christopher, and Jorg Schwenk. ``Lessons Learned From Previous SSL/TLS Attacks A Brief Chronology Of Attacks And Weaknesses.'' eprint.iacr.org. Ruhr-University, n.d. Web. 22 April 2014. \verb#<https://eprint.iacr.org/2013/049.pdf>#.
\bibitem{nistsp80090a} ``NIST SP 800-90A: Recommendation for Random Number Generatation Using Deterministic Random Bit Generators'' \textit{National Institute of Standards and Technology}. January 2012. Web. April 2014.
\bibitem{oppliger} Oppliger, Rolf. \textit{SSL and TLS theory and practice}. Boston: Artech House, 2009. Print.
\bibitem{rescorla} Rescorla, Eric. \textit{SSL and TLS: designing and building secure systems}. Boston: Addison-Wesley, 2001. Print.
\bibitem{trappe} Trappe, W.\ and Washington, L.C. \textit{Introduction to Cryptography with Coding Theory}. 2nd ed. Upper Saddle River: Prentice Hall, 2006. Print.
\end{thebibliography}
